\chapter{Practical Insights and Reflections}
     \hspace*{0.6cm}Our field trip to the Geological Museum of Ho Chi Minh City left us deeply impressed and enthusiastic about the wealth of knowledge and experiences we acquired. The opportunity to directly observe, research, and access geological specimens, mineral samples, and ancient fossils enabled us to gain a profound understanding of the theoretical concepts previously encountered only in textbooks and lecture halls. This excursion was far more than a simple extracurricular activity; it served as a vivid, practical lesson. By witnessing firsthand the precious gemstones and minerals characteristic of different regions across the country, we developed a greater appreciation for the diversity and significant value of Vietnam's geological resources.
     \newline
     \hspace*{0.6cm}We are particularly engaging to the enthusiastic guidance of M.Sc. Dong Uyen Thanh and M.Sc. Tran Thi Mai Huong, who helped us clarify the critical role of the geological sector in national construction and defense, particularly within the modern context of economic development tied to natural resource exploitation. The museum effectively acts as a bridge between theory and practice in geological research. For students in fields such as Geology, Environmental Engineering, and Earth Science—including our group from Ho Chi Minh City University of Technology (HCMUT)—this space functions as an "open laboratory," allowing for the visualization of academic knowledge through tangible specimens.
     \newline
     \hspace*{0.6cm}Moreover, the Geological Museum of Ho Chi Minh City is not only a repository for the country's precious geological heritage but also a center for knowledge, education, and inspiration for young science enthusiasts. In the context of global challenges such as climate change and natural resource management, a deep understanding of geology and minerals is vital for forming a mindset of sustainable development within the community. Through this trip, we have become more aware of the importance of conserving geological specimens and recognize our future responsibility in advocating for the rational and sustainable exploitation of natural resources.